Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-20 papers/B1555_EdgeOn/B1555_letter.tex
add radio scatter discussion

\hline
	& MERLIN & VLA & \multicolumn{3}{c}{Model}\\
		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
A/B			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
A/C 		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
A/D			&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\

@@

Discussions on substructure searching in strong lensing system are mostly done by multiple images of lensed quasar. In the ideal case (no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential. Numerical simulations have examined this idea with known lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure origined flux anomaly, including our target B1555+375. They conclude B1555+375 with improper lens model. This result can be supported by SHARP K-band image, which an edge-on disk lies across between the radio merging double A \& B. A more complex lens model (e.g. include an exponential disk) must be applied on B1555+375.

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modelling, substructure is not neccessary to presence and a  exponential disk with high ellipcity well explains the observed flux ratio anomaly. This indicates that in B1555+375, flux ratio anomaly is caused by structure of lens galaxy itself rather than substructure. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars. A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar. Thus, one must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real  substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. For precise estimation on substurcture population, mass function, or any derived properties from strong lensed flux anomalous quasars, non-substructure effects are important to be understood beforehand.

>>>>

\hline
	& MERLIN & VLA & \multicolumn{3}{l}{Model}\\
		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
$f_A/f_B$			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
$f_A/f_C$		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
$f_A/f_D$		&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\

@@

Discussions on substructure searching in strong lensing system are mostly done by multiple images of lensed quasar. In the ideal case (no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential. Numerical simulations have examined this idea with known lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure origined flux anomaly, including our target B1555+375. They conclude B1555+375 with improper lens model. This result can be supported by SHARP $K^{\prime}$ band image, which an edge-on disk lies across between the radio merging double A \& B. A more complex lens model (e.g. include an exponential disk) must be applied on B1555+375.

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models predict the radio image positions and flux ratio anomaly between components A and B, which the 1-SIE model in \citet{Marlow} fails. Since radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}, our successful modelling indicates that the structure from lens galaxy itself can cause radio flux ratio anomalies. An edge-on disk with high ellipcity can well explain the observed flux ratios and substructure is not neccessary to presence. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars. A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future. One must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real  substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. For precise estimation on substurcture population, mass function, or any derived properties from strong lensed flux anomalous quasars, non-substructure effects are important to be understood beforehand.
